Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-13 eswc-2012/phdsymp.tex
rewrite introduction
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@84 43ef1190-90fd-4dd7-a769-d0121f02b80e

I intend to investigate possible remedies to this problem by using
statistical techniques.

Since the main objective of the proposed work is to create systems
that have sufficient performance for practical applications, it is of
paramount importance to have methodology that can rigorously rank
implementations based on performance.

However, I have found the current state of the art in SPARQL benchmarking
lacking in its use of statistics, which motivates two distinct
directions of work: \emph{Statistical experimental planning and execution in
benchmarking} and \emph{statistical methods to optimize SPARQL queries
in a federated regime}.

I am still in an early phase of my work, and I have not yet started to
explore the scientific literature around SPARQL Federation to any
depth, currently focusing my efforts on benchmarking. Therefore, this
paper also focuses on benchmarking rather than the more long-term goal
of SPARQL Federation.

>>>>

To help optimize, SPARQL endpoints should expose details about both
data and performance characteristics of the engine itself. The
proposed work has two focal points: \emph{Statistical digests of
  data for optimizations} and \emph{benchmarking SPARQL engines}.

The focus on SPARQL benchmarking is not just motivated from the
optimization perspective, as I have found the current state of the art
in SPARQL benchmarking lacking in its use of statistics. The emphasis
in the present paper is on statistics in benchmarking with the purpose
of putting it on a firmer foundation from a hypothesis testing
perspective.

I am still in an early phase of my work, and I have not yet started to
explore the scientific literature around SPARQL Federation to any
depth, currently focusing my efforts on benchmarking. The long-term
goal of my work is SPARQL Federation, but it is a minor concern in
this paper.
